---
title: "assignment_1"
output: github_document
date: "2022-10-31"
---

# Assignment 1 by Mengyang Guo

### Setup

Here, I load the necessary package

```{r}

suppressPackageStartupMessages(library(datateachr)) 
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(broom))
suppressPackageStartupMessages(library(palmerpenguins))
suppressPackageStartupMessages(library(testthat))
suppressPackageStartupMessages(library(digest))
```

### Exercise 1: Make a Function

In this exercise, I make a function to scale the dataset by median value in each category. I would like to make this function because I repeated this process for many, many times for the data analysis in STAT 545A. So I'm consider making a function for this action. Below are some features of the function:

-   The input is df (the dataset) and category (based on which I calculate the median for each category).

-   Before start, the function checks whether the input is a data frame or not. Next, it cleans the data in the following 3 steps

-   First, it calculates the median value for each category (e.g., gender).

-   Second, it scales all the numeric variables in the dataset by each variable's median number in each category. For example, the weight of a female student is 65kg. Given the cauculated median female student weight of 60kg, I calculate the student's scaled weight to be (65-60)/60, which is 0.083. This means that she is 8.3% overweight relative to the median female weight.

-   Third, I drop all the missing values.

-   The output of this function is the cleaned dataset.

See the code below:

```{r}
scale_by_median <- function(df,category)
{
#put category enquo
category <- enquo(category)

#give a warning if df is not a dataset 
if(!is.data.frame(df)){
    stop('I am so sorry, but this function only works for data frame input!\n',
         'You have provided an object of class: ', class(df)[1])
}

#Cleaning the dataset following the previously mentioned 3 steps
df %>%
  group_by(!!category) %>%
 mutate(across(where(is.numeric), ~ (.x-median(.x,na.rm=TRUE))/median(.x,na.rm=TRUE)))%>%
  drop_na () -> scaled_data

#returns cleaned dataset
  return(scaled_data)
}
```

### Exercise 2: Document the function

In this exercise, I will document my function using [roxygen2 tags](https://roxygen2.r-lib.org/articles/rd-formatting.html)

```{r}

#'@title A function to scale each observation
#'@description This function scales all of its numeric variables. Specifically, I scale each observation the median number in the category.
#'@param df Dataframe(I use df as the abbreviation of data frame)
#'@param category Categorial variable (based on which I cauculate the median for each group)
#'@return the funtion returns the scaled dataset based on input \code{df} and \code{category}

scale_by_median <- function(df,category)
{
#put category enquo
category <- enquo(category)

#give a warning if df is not a dataset 
if(!is.data.frame(df)){
    stop('I am so sorry, but this function only works for data frame input!\n',
         'You have provided an object of class: ', class(df)[1])
}

#Cleaning the dataset following the previously mentioned 3 steps
df %>%
  group_by(!!category) %>%
 mutate(across(where(is.numeric), ~ (.x-median(.x,na.rm=TRUE))/median(.x,na.rm=TRUE)))%>%
  drop_na () -> scaled_data

#returns cleaned dataset
  return(scaled_data)
}
```

### Exercise 3: Include Examples

In the first example, I scale the penguins dataset. I only use the first five columns to illustrate (because it makes sense to scale these numeric variables, rather than some other numeric ones). The output data looks good to me. All the numeric variables are scaled.

```{r}
penguins[1:5]->penguins_subsample

# I scale each observation by the median number in its species.

scale_by_median(penguins_subsample,species)

```

In the second example, I scale the cancer dataset. I only use the 2-6 columns to illustrate (because the first column is the numeric cancer ID and it doesn't make sense to scale the cancer ID). The output data looks good to me. All the numeric variables are scaled.

```{r}
datateachr::cancer_sample[2:6]->cancer_subsample


# I scale each observation by the median number in its diagnosis.

scale_by_median(cancer_subsample,diagnosis)
```

In the third example, ***I intentionally show error!*** I show that this dataset stop working if the input is not a data frame. It successfully alters me that "*I am so sorry, but this function only works for data frame input!, You have provided an object of class: character*"

```{r, error=TRUE}

# I will first define a string variable
string_variable<-"adfs"

# I use it as input
scale_by_median(string_variable,diagnosis)

## I succefully find error!
```

***I intentionally showed this error!***

### 

### Exercise 4: Test the Function

I will test three things using the cancer data:

-   I test whether the calculated values on row ten is accurate.

-   I test whether the total number of rows is correct

-   I test whether I have successfully dropped all the missing values

    I will first calculate the values on row ten and the total number of rows

```{r}

# I run the code without using functions to cauculate the row ten numbers

cancer_subsample %>%
  group_by(diagnosis) %>%
 mutate(across(where(is.numeric), ~ (.x-median(.x,na.rm=TRUE))/median(.x,na.rm=TRUE)))%>%
  drop_na () -> scaled
  digest(unname(as.matrix(scaled)[10,]))

# I run the code to get the total number of rows 
  
nrow(scaled)
  
```

The following output suggest that the row 10 should be "24948aec6fc35f41a44b2fb6d2d8b61c" and I should have 569 rows.

**I formally test it below:**

```{r}

test_that("Testing my function", {
    expect_equal(digest(unname(as.matrix(scale_by_median(cancer_subsample,diagnosis))[10,])),  "24948aec6fc35f41a44b2fb6d2d8b61c")
    expect_equal(nrow(scale_by_median(cancer_subsample,diagnosis)),  569)
    expect_false(any(is.na(scale_by_median(cancer_subsample,diagnosis))))
})

```

**The test was passed!**
