---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# scaling function

<!-- badges: start -->
<!-- badges: end -->

The goal of scale_by_median is to scales all the numeric variables in the dataset by each variable's median number in each category. It achieves three goals: 1) check if the input is a dataset 2) scales all the numeric variables in the dataset by each variable's median number in each category, 3) delete missing values.

## Installation

You can install the development version of scale_by_median from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-MengyangBillyGuo")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## Load the package
library(scaling)

## I use mtcars as example.

## The following code shows the distance and horse power numbers fully scaled by median number for each cylinder category. 
scale_by_median(mtcars,mtcars$cyl)[3:4]

## Zeros means they are the median numbers.

```


